---
title: "Test Rmd to HTML Docker Container"
author: '[Frank Jung](https://www.linkedin.com/in/frankjung/)'
date: "`r format(Sys.time(), format='%d %b %Y')`"
labels: '[test, rmd, Docker]'
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
```

## Test Plot

This is a simple test of the Rmd to HTML Docker container.
It should render this Rmd file to HTML without any issues.

```{r cars, echo=TRUE}
summary(cars)
ggplot(cars, aes(x = speed, y = dist)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "Speed vs Distance", x = "Speed (mph)", y = "Distance (ft)")
```

## Test Mathematics - Prove that $\log_2 3$ is irrational

I start by assuming $\log_2 3$ is rational.

That means there exist positive integers $a > 0$ and $b > 0$ such that:

$$\log_2 3 = \frac{a}{b}$$

$$2^{\frac {a}{b}} = 3$$

$$2^a = 3^b$$

Let $a = k + 1$, and replace:

$$2^{k+1} = 3^b$$

Factor out 2:

$$2 \times 2^k = 3^b$$

Because $a$ is a positive integer, $2^a$ is 2 multiplied by itself $a$ times, so the left side is even.

Because $b$ is a positive integer, $3^b$ is 3 multiplied by itself $b$ times, so the right side is odd.

An even number cannot equal an odd number, so I have reached a contradiction.

Therefore, $\log_2 3$ is irrational. $\square$
